\LARGE \bf Autonomous Object Manipulation using a Soft Planar Grasping Manipulator

### 2015-10-12 SoRo reviewer comments/Reviewer Comments Reply 15-10-10.tex

\section{Reviewer 1's Comments}

\textit{This paper discusses an autonomous object manipulation algorithm using a soft planar grasping manipulator.}

\subsection{Contribution Discussion}
\textit{Several major issues with the paper hold it back. First, the contribution of the paper seems very minor. A considerable amount of the paper is already covered in the work\cite{marchese2014whole} \cite{marchese2014design} \cite{marchese2015recipe}, which involves the design of the robot, the recipe to create the robot, and the whole-arm motion planning. The contribution of this work is the grasping algorithm itself, which is a preplanned sequence of robot curvatures. In light of the whole arm motion planner in  \cite{marchese2014whole}, this contribution seems minor when adding in a (circular) object.  The algorithm itself is implemented as a state-machine method, and with 4 or 5 states and seems trivial. Only one experimental test is performed to demonstrate the algorithm, and no quantitative error metrics are provided.}

@@

In that case, the control loop can not function properly until the occlusion disappears. 
The external localization system could be replaced with another method for localizing the manipulator and the object in the workspace.
For example, proprioceptive sensors within the segments could solve this issue partially. 
A first step towards proprioceptive sensing was done for three soft fingers arranged as a hand in reference \cite{homberg2015haptic}.

@@

The sentence was confusing, we clarified the manuscript.
%
\subsection{Contribution 1}
\textit{Section 1.2 Contribution 1 seems entirely described in \cite{marchese2014whole} and \cite{marchese2015recipe}. Contribution 4 seems obvious that force sensing nor accurate positioning is required to manipulate objects.}

@@

%
Contribution 1 is different to previous contributions: Reference \cite{marchese2014whole} only presents a 6 segment soft arm that can move on a plane, not interaction or manipulation capabilities with objects are shown. The paper deals with the changing body shape of the soft arm when moving it around on a plane. Reference \cite{marchese2015recipe} discusses fundamental actuator morphologies and presents recipes on combining those morphologies, but an actually controllable 7 DOF arm is not detailed in that work. In this manuscript, we plan for an enveloping grasp of an unknown object in the plane and demonstrate pick-and-place from uncertain locations. We made clarifications to the contributions sections accordingly.

@@

Thank you for this comment. We moved the labels on the figure. Also, we added to the paper why the physical frame is important to have a mobile presentation platform that can keep the system together, hold the tracking cameras rigidly in place, and does not require recalibration of the tracking cameras. 
%
\subsection{Fabrication Steps Detailing}
\textit{Section 3.1-3.2 These sections are completely described in \cite{marchese2015recipe}  and comes off as a recipe to make the manipulator, which is the contribution of \cite{marchese2015recipe}, and therefore should not be reproduced in the main text. Figure 4 and Table 1. Pulled from \cite{marchese2015recipe} seem unnecessary. Furthermore Table 1 does not fit the column.}

@@

The weights are set by the matrix $\mathbf{R}$. The variables to optimize for are $\phi$ and $\kappa$. All parameters are introduced as inputs to the algorithm. We revised the manuscript to clarify this point and make it easier to find the optimization equation. 
%
\subsection{Algorithm Difference}
\textit{I also find it difficult to see exactly the difference between the algorithm presented here and the one in \cite{marchese2014whole}. While grasping is indeed is one objective, that seems to be realized by a curvature objective.} 
We thank the reviewer for this comment. We revised the exposition within the "existing procedures section" to highlight the differences between the two approaches. The algorithm in \cite{marchese2014whole} is about planning the motion of a soft arm without a gripper through a maze at a centerline while taking the arms bulging shape as a trapezoidal into account. The approach does not work for approaching and grasping objects, because a tip trajectory for successfully moving towards the object is not known, but needs to be generated by posing and solving a new optimization problem. That trajectory needs to avoid pushing the object away with the manipulator trunk when approaching it with the soft gripper at its end. In this paper we present an algorithm for approaching an object by following along concentric lines, which are further and further decreasing in size until object size is achieved. The non-linear optimization is finding tangent poses along these lines using non-linear optimization and then follows down those concentric lines, which implicitly guarantees the arms pose to stay convex – since the circles are convex themselves.
\subsection{Optimization Constraints}
\textit{Section 4.2 Is the optimization function over or underconstrained? Will you always find a solution? What happens if you don’t find a solution?}
We added to the manuscript: "The optimization only becomes over-constrained if it has to find an arm pose outside of the arm's reachable workspace. That occurs if the object was user-placed outside the workspace. Before performing the optimization, a feasability check is performed using the arm's forward kinematics."

@@

\subsection{Clearer Fabrication Process Description}
\textit{I found the description of the fabrication process for the gripper to be slightly confusing. I think more annotations on figure 3 (such as point 1 or c, etc) and referring to those annotations in the description could make it clearer. Especially since this is listed as a major contribution.}
%
Figure 3’s point 1 and c were modified according to your suggestion and more descriptive notes were added to the fabrication figure and the description in the paper.

@@

\item \textit{Is using motion tracking realistic for some of the scenarios you suggest? I would guess not, but what is the future for state estimation? Existing sensors? Or are new sensors needed?}
%
We added:
"It is worth mentioning that the exteroceptive tracking system has the disadvantage that a full occlusion of one or more markers can cause the tracking system to temporarily loose track of a measured arm segment. In that case, the control loop can not function properly until the occlusion disappears. Proprioceptive sensors within the segments can solve this issue. A first step towards proprioceptive sensing was done for three soft fingers arranged as a hand in reference \cite{homberg2015haptic}."

@@

We revised the text to clarify this point, we added in the multi-segment arm section: 
"As was shown in [13] through the characterization of various actuator morphologies, the concatenation of soft cylindrical segments is most suitable to build up a robot arm that can create high blocking forces per fluid energy inserted."
We also added to the same section:
"Using six segments, the $\pm 60^\circ$ joint limit does not prohibit the robot to reach its own base. Calculating the forward kinematics, see \texttt{forwKin()} procedure in Algorithm 1, for the 6 DOF arm with a segment length of 6.27\unit{cm} and an extreme curvature of $\kappa = \frac{60/180 \pi}{0.0627\unit{m}} = 16.7\frac{1}{\unit{m}}$ shows that the tip of the robot can reach its root at a full curl." 

### 2015-10-12 processing_control.tex
final comments

The planning algorithm presented in \cite{marchese2014whole} was developed to plan the motion of a soft arm  without gripper through a confined environment. 
The optimization constraints and state machine setup in that work is significantly different and not applicable to the grasping shown here. 
Therefore, a new planner is presented in the following section.

@@

\rkk{The procedure \texttt{findOptimalConfig($r_a$)}} is posed as a nonlinear optimization \rkk{problem}. 
Here, the objective function represents the summation of independently weighted manipulator curvatures \rkk{$\boldsymbol{\kappa} - \boldsymbol{\kappa}_{\textrm{off}}$.}
\rkk{The weights are set by the matrix $\mathbf{R}$.}
\rkk{The variables to optimize for are $\phi$ and $\kappa$.}
The optimization constraints \rkk{cause} the manipulator's tip to lie on and to be tangent to the approach circle. 
\rkk{The constraints also ensure that the manipulator segment curvatures do not exceed the single soft actuator limits.}
\rkk{Furthermore,} this \rkk{procedure} leverages the arm's forward kinematics \texttt{forwKin()} defined in \cite{marchese2014design} and reproduced \rkk{in the last section} of Algorithm~\ref{alg:planGrasp} for convenience.

>>>>

\rkk{The algorithm presented in \cite{marchese2014whole} is about planning the motion of a soft arm without a gripper through a maze at a centerline while taking the arms bulging shape into account. The approach does not work for approaching and grasping objects, since a tip trajectory for successfully moving towards the object is not known, but needs to be generated by posing and solving a new optimization problem. This tip trajectory has to avoid that the manipulator trunk pushes the object prematurely away when approaching it. Therefore, a new planner had to be developed and is presented in the following section.}

@@

\rkk{The procedure \texttt{findOptimalConfig($r_a$)}} is posed as a nonlinear optimization \rkk{problem}. 
Here, the objective function represents the summation of independently weighted manipulator curvatures \rkk{$\boldsymbol{\kappa} - \boldsymbol{\kappa}_{\textrm{off}}$.}
\rkk{The weights are set by the matrix $\mathbf{R}$.}
\rkk{The variables to optimize for are $\phi$ and $\kappa$.}
The optimization constraints \rkk{cause} the manipulator's tip to lie on and to be tangent to the approach circle. 
\rkk{The constraints also ensure that the manipulator segment curvatures do not exceed the single soft actuator limits.}
\rkk{Furthermore,} this \rkk{procedure} leverages the arm's forward kinematics \texttt{forwKin()} defined in \cite{marchese2014design} and reproduced \rkk{in the last section} of Algorithm~\ref{alg:planGrasp} for convenience. 
\rkk{The optimization only becomes over-constrained if it has to find an arm pose outside of the arm's reachable workspace. That occurs if the object was user-placed outside the workspace. Before performing the optimization, a feasability check is performed using the arm's forward kinematics.}
